---
title: "Weight of Fish"
author: "Trevor Ragazzo"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```


```{r}
All_Fish = read.csv(file="Fish.csv")
```


```{r}
Perch = filter(All_Fish,Species=="Perch")
```

```{r}
Perch = select(Perch, -Species)
```


# Predicting Fish Weight




## Perch


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```



### Best Models

The best model for perch is Width and Height.

### Best Two regressor model

The best two regressor model is also width and height

## Pike

```{r}
Pike = filter(All_Fish,Species=="Pike")
```

```{r}
Pike = select(Pike, -Species)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models

The best model is the L1,L2,L3,H,W because we see this is rated highest on the graph. It has a .98 rateing compared to everything else. 

### Best Two regressor model

The best two regressor models are L1 and L3 because they ahd the biggest adjustment to rsquared.

## Roach

```{r}
Roach = filter(All_Fish,Species=="Roach")
```

```{r}
Roach = select(Roach, -Species)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models

The best model that we see is L3, and W. This is because it is at the top of the graph, and only W is near the combo.

### Best Two regressor model

The best two regressor model is still L3, and W. This is the best model out of all the other ones.

## Final Summary Statements

In conclusion I have seen almost a similar result in all graphs, I have seen Width being in every graph and the best model. Overall it shows width plays a big factor in measuring the fish as shown in these graphs. 
